A meta-analysis of mental rotation ability in the first years of life

### 2022-04-21 code/analysis.Rmd
Update main, gender, and interaction models
- Making `gender` a categorical variable
- Contrast coding for gender
- Use `experiment` as a unique group-article identifier

    # Convert mean sample age from days to months and center
    age_months = age_mean / 30.417,
    age_months_c = age_months - mean(age_months, na.rm = TRUE),

@@

# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    vi = ((2 * (1 - r_assumed)) / ni) + (gi^2 / (2 * ni)),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article, group, gender_split, gi, ni, vi, sei, age_months_c, female_percent
  ) -> dat_r

@@

```{r, compute_meta, echo=TRUE}
# # Two-level model
# res_rma <- rma(
#   gi, vi,
#   data = dat_r,
#   slab = experiment_ids
# )
# print(res_rma)
# forest(res_rma)

# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_ml)
# forest(res_ml)

# # Saving the forest plot
# pdf("forest.pdf", width = 12, height = 12)
# forest(res_ml)
# dev.off()

@@

# Meta-regression with age
res_age <- rma.mv(
  gi, vi,
  mods = ~age_months_c,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_age)
# forest(res_age)

# Meta-regression with gender
res_gender <- rma.mv(
  gi, vi,
  mods = ~female_percent,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_gender)
# forest(res_gender)

# Meta-regression with age, gender, and their interaction
res_full <- rma.mv(
  gi, vi,
  mods = ~ age_months_c * female_percent,
  random = ~ 1 | article / group,
  data = dat_both_mixed,
  slab = paste(article, group, sep = ", ")
)
print(res_full)
# forest(res_full)
```

@@

# Run prior predictive simulation
res_prior <- brm(
  gi | se(sei) ~ 1 + (1 | article / group),
  data = dat_both_mixed,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 2000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(res_prior, sample_prior = FALSE)
summary(res_brm)
# plot(res_brm)

# Sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```

>>>>

    # Add unique experiment identifier
    experiment = str_c(article, group, seq = ", "),

    # Convert gender to a categorical variable
    gender = case_when(
      female_percent == 1.0 ~ "female",
      female_percent == 0.0 ~ "male",
      !is.na(female_percent) ~ "mixed"
    ) %>% factor(levels = c("mixed", "female", "male")),

    # Convert mean sample age from days to months and center
    age_months = age_mean / 30.417,
    age = age_months - mean(age_months, na.rm = TRUE),

@@

# Compute standard error of Cohen's d based on assumed correlation
# This will need a sensitivity analysis
r_assumed <- 0.5
dat %>%
  mutate(
    ni = sample_size,
    vi = ((2 * (1 - r_assumed)) / ni) + (gi^2 / (2 * ni)),
    sei = sqrt(vi)
  ) %>%
  filter(!is.na(gi)) %>%
  select(
    article,
    group,
    experiment,
    gender_split,
    gi,
    ni,
    vi,
    sei,
    gender,
    age
  ) -> dat_r

@@

```{r, compute_meta, echo=TRUE}
# Three-level model
res_ml <- rma.mv(
  gi, vi,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_ml)
# forest(res_ml)

@@

# Apply sliding difference contrast coding for the gender categories
# This means that the Intercept will be the grand mean (i.e., the average across
# studies) whereas the betas will test female vs. mixed and male vs. female
(contrasts(dat_both_mixed$gender) <- MASS::contr.sdif(3))

# Meta-regression with gender
res_gender <- rma.mv(
  gi, vi,
  mods = ~ gender - 1,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_gender)
# forest(res_gender)

# Pairwise comparison between the gender groups
anova(res_gender, X = rbind(c(-1, 1, 0), c(-1, 0, 1), c(0, -1, 1)))

# Meta-regression with age
res_age <- rma.mv(
  gi, vi,
  mods = ~age,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_age)
# forest(res_age)

# Meta-regression with gender, age, and their interaction
res_full <- rma.mv(
  gi, vi,
  mods = ~ gender * age,
  random = ~ 1 | article / experiment,
  data = dat_both_mixed,
  slab = experiment
)
print(res_full)
# forest(res_full)
```

@@

# Run prior predictive simulation
res_prior <- brm(
  gi | se(sei) ~ 1 + (1 | article / experiment),
  data = dat_both_mixed,
  prior = prior_c,
  sample_prior = "only",
  save_pars = save_pars(all = TRUE),
  chains = 4,
  iter = 2000,
  cores = 4,
  control = list(adapt_delta = 0.99)
)
summary(res_prior)
# plot(res_prior)

# Run Bayesian multilevel model
res_brm <- update(res_prior, sample_prior = FALSE)
summary(res_brm)
# plot(res_brm)
```

```{r, prior_sens, eval=FALSE}
# Prior sensitivity analysis
list(
  "interept_uninformative" = c(
    set_prior("uniform(-3, 3)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "interept_informative" = c(
    set_prior("normal(0, 0.2)", class = "Intercept"),
    set_prior("cauchy(0, 0.3)", class = "sd")
  ),
  "sd_uninformative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("uniform(0, 10)", class = "sd", ub = 10)
  ),
  "sd_informative" = c(
    set_prior("normal(0, 1)", class = "Intercept"),
    set_prior("student_t(10, 0, 0.2)", class = "sd")
  )
) %>%
  map(function(prior_sens) update(res_brm, prior = prior_sens)) -> res_sens
map(res_sens, summary)
```
